\Large Inferential Analysis of the Supreme Court Citation Network

### 2018-03-20 Tex/paper.tex
new holdout experiment results

 \section{Empirical Analysis}
Our three data sources for this study include the SCDB, Martin-Quinn scores, and Supreme Court citation data provided by Courtlistener ?cite. We limit the Supreme Court terms included in our analysis to those that are covered by all three of these data source (1937--2015).  The Supreme Court citation network from $1937 - 2015$ consists of $9,841$ cases. The breakdown of the data by the Court's Chief Justice is presented in Table \ref{tab:chiefs}. The network has a total of $110,742$ ties. The number of triangles in the network is $246,134$. The in- and outdegree distributions (i.e., the distributions of the number of citations sent and received by cases, respectively), are visualized in Figure \ref{degree_dist}. The maximum indegree is $228$ and the maximum outdegree is $162$.

\begin{table}[htp]
\centering
\begin{tabular}{|
>{\columncolor[HTML]{C0C0C0}}l |l|l|l|}
\hline
{\color[HTML]{333333} } & \cellcolor[HTML]{C0C0C0}{\color[HTML]{333333} Terms} & \cellcolor[HTML]{C0C0C0}{\color[HTML]{333333} Total Number Cases} & \cellcolor[HTML]{C0C0C0}{\color[HTML]{333333} Cases/Term} \\ \hline
CE Hughes*              & 1937 - 1941                                          & 628                                                               & 125.6                                                     \\ \hline
HF Stone                & 1942 - 1946                                          & 756                                                               & 151.2                                                     \\ \hline
FM Vinson               & 1946 - 1953                                          & 786                                                               & 98.25                                                      \\ \hline
E Warren                & 1954 - 1969                                          & 2123                                                              & 124.88                                                     \\ \hline
WE Burger               & 1970 - 1986                                          & 2755                                                              & 153.06                                                     \\ \hline
W Rehnquist            & 1987 - 2005                                          & 2004                                                              & 105.47                                                      \\ \hline
J Roberts **           & 2006 - 2015                                          & 789                                                              & 78.9                                                      \\ \hline
\end{tabular}
\caption[caption]{For the time range of interest (1937 - 2015) this table displays the chief justices, the time range they served as chief justice, the number of cases in their time range as well as the average number of cases per year.\\\hspace{\textwidth} * CE Hughes served as chief justice from 1930 - 1941. \\\hspace{\textwidth} ** J Roberts still serves as chief justice (2/2018).}
\label{tab:chiefs}
\end{table}

@@

  \begin{figure}[H]
  \begin{tabular}{cc}
 (a) MQ Score Difference & (b) Ideological Breadth \\
\includegraphics[width = 0.475\textwidth, trim= 0.1cm 1cm 0.5cm .45cm,clip=true]{images/mq_coef_trend.pdf} & \includegraphics[width = 0.475\textwidth, trim= 0.1cm 1cm 0.5cm .45cm,clip=true]{images/absdiffmq_coef_trend.pdf} \\

  (c) Same Issue & (d) Majority Size \\
\includegraphics[width = 0.475\textwidth, trim= 0.1cm 1cm 0.5cm .45cm,clip=true]{images/sameissue_coef_trend.pdf} & \includegraphics[width = 0.475\textwidth, trim= 0.1cm 1cm 0.5cm .45cm,clip=true]{images/numberjusticespro_coef_trend.pdf} \\

   (e) Reciprocity & (f) Transitivity \\
\includegraphics[width = 0.475\textwidth, trim= 0.1cm 1cm 0.5cm .45cm,clip=true]{images/mutual_coef_trend.pdf} & \includegraphics[width = 0.475\textwidth, trim= 0.1cm 1cm 0.5cm .45cm,clip=true]{images/triangle_coef_trend.pdf} \\

    (g) Activity & (h) Popularity \\
\includegraphics[width = 0.475\textwidth, trim= 0.1cm 1cm 0.5cm .45cm,clip=true]{images/o2star_coef_trend.pdf} & \includegraphics[width = 0.475\textwidth, trim= 0.1cm 1cm 0.5cm .45cm,clip=true]{images/i2star_coef_trend.pdf} \\

@@

\begin{table}[H]
\centering
\begin{tabular}{rllll}
\hline \hline
& \multicolumn{2}{c}{Independent Model} & \multicolumn{2}{c}{Full Model} \\
   \hline
 & mean & range & mean & range \\ 
  \hline
precision & 0.5582 & (0.5509, 0.5751) & 0.8678 & (0.865, 0.8721) \\ 
  recall & 0.0995 & (0.0953, 0.1043) & 0.5937 & (0.588, 0.6027) \\ 
  F1 score & 0.1688 & (0.163, 0.1766) & 0.7051 & (0.7009, 0.7117) \\ 
   \hline \hline
\end{tabular}
\caption{The predictive performance of the directed dyadic models with linear trends, over ten 80/20 train/test splits.}
\label{tab:prediction_linear}
\begin{tabular}{rllll}
\hline \hline
& \multicolumn{2}{c}{Independent Model} & \multicolumn{2}{c}{Full Model} \\
   \hline
 & mean & range & mean & range \\ 
  \hline
precision & 0.8827 & (0.878, 0.8876) & 0.8672 & (0.8629, 0.8731) \\ 
  recall & 0.5316 & (0.5255, 0.5408) & 0.5939 & (0.5872, 0.6008) \\ 
  F1 score & 0.6635 & (0.6594, 0.6709) & 0.705 & (0.7008, 0.7118) \\ 
   \hline \hline
\end{tabular}
\caption{The predictive performance of the directed dyadic models with quadratic trends, over ten 80/20 train/test splits.}
\label{tab:prediction_quadratic}
\begin{tabular}{rllll}
\hline \hline
& \multicolumn{2}{c}{Independent Model} & \multicolumn{2}{c}{Full Model} \\
   \hline
 & mean & range & mean & range \\ 
  \hline
precision & 0.8745 & (0.8718, 0.8769) & 0.8667 & (0.8649, 0.8684) \\ 
  recall & 0.5732 & (0.5693, 0.5783) & 0.5949 & (0.5902, 0.5981) \\ 
  F1 score & 0.6925 & (0.6892, 0.6969) & 0.7056 & (0.7025, 0.7083) \\ 
   \hline \hline
\end{tabular}
\caption{The predictive performance of the directed dyadic models with cubic trends, over ten 80/20 train/test splits.}
\label{tab:prediction_cubic}
\begin{tabular}{rllll}
\hline \hline
& \multicolumn{2}{c}{Independent Model} & \multicolumn{2}{c}{Full Model} \\
   \hline
 & mean & range & mean & range \\ 
  \hline
precision & 0.8769 & (0.8738, 0.881) & 0.8687 & (0.8646, 0.8718) \\ 
  recall & 0.583 & (0.5754, 0.5896) & 0.5956 & (0.5895, 0.6008) \\ 
  F1 score & 0.7004 & (0.6946, 0.7042) & 0.7067 & (0.7018, 0.7098) \\ 
   \hline \hline
\end{tabular}
\caption{The predictive performance of the directed dyadic models with quartic trends, over ten 80/20 train/test splits.}
\label{tab:prediction_quartic}
\end{table}

>>>>

 \section{Empirical Analysis}
Our three data sources for this study include the Supreme Court Database (SCDB), Martin-Quinn scores, and Supreme Court citation data provided by Courtlistener ?cite. We limit the Supreme Court terms included in our analysis to those that are covered by all three of these data source (1937--2015)\footnote{There were 145 cases that were listed in the SCDB but could not be matched to a case in the Courtlistener data. We decided to exclude these 145 cases from our model.}. The Supreme Court citation network from $1937 - 2015$ consists of $9,945$ cases. The breakdown of the data by the Court's Chief Justice is presented in Table \ref{tab:chiefs}. The network has a total of $111,986$ ties. The number of triangles in the network is $250,717$ and the number of mutual ties is $56$. The in- and outdegree distributions (i.e., the distributions of the number of citations sent and received by cases, respectively), are visualized in Figure \ref{degree_dist}. The maximum indegree is $230$ and the maximum outdegree is $162$.

\begin{table}[htp]
\centering
\begin{tabular}{|
>{\columncolor[HTML]{C0C0C0}}l |l|l|l|}
\hline
{\color[HTML]{333333} } & \cellcolor[HTML]{C0C0C0}{\color[HTML]{333333} Terms} & \cellcolor[HTML]{C0C0C0}{\color[HTML]{333333} Total Number Cases} & \cellcolor[HTML]{C0C0C0}{\color[HTML]{333333} Cases/Term} \\ \hline
CE Hughes*              & 1937 - 1941                                          & 628                                                               & 125.6                                                     \\ \hline
HF Stone                & 1942 - 1946                                          & 756                                                               & 151.2                                                     \\ \hline
FM Vinson               & 1946 - 1953                                          & 789                                                               & 98.63                                                      \\ \hline
E Warren                & 1954 - 1969                                          & 2149                                                              & 126.41                                                     \\ \hline
WE Burger               & 1970 - 1986                                          & 2805                                                             & 155.83                                                     \\ \hline
W Rehnquist            & 1987 - 2005                                          & 2022                                                              & 106.42                                                      \\ \hline
J Roberts **           & 2006 - 2015                                          & 796                                                              & 79.6                                           \\ \hline
\end{tabular}
\caption[caption]{For the time range of interest (1937 - 2015) this table displays the chief justices, the time range they served as chief justice, the number of cases in their time range as well as the average number of cases per year.\\\hspace{\textwidth} * CE Hughes served as chief justice from 1930 - 1941. \\\hspace{\textwidth} ** J Roberts still serves as chief justice (3/2018).}
\label{tab:chiefs}
\end{table}

@@

  \begin{figure}[H]
  \begin{tabular}{cc}
 (a) MQ Score Difference & (b) Ideological Breadth \\
\includegraphics[width = 0.475\textwidth, trim= 0.1cm 1cm 0.5cm .45cm,clip=true]{images/mq_coef_trend_linear.pdf} & \includegraphics[width = 0.475\textwidth, trim= 0.1cm 1cm 0.5cm .45cm,clip=true]{images/absdiffmq_coef_trend_linear.pdf} \\

  (c) Same Issue & (d) Majority Size \\
\includegraphics[width = 0.475\textwidth, trim= 0.1cm 1cm 0.5cm .45cm,clip=true]{images/sameissue_coef_trend_linear.pdf} & \includegraphics[width = 0.475\textwidth, trim= 0.1cm 1cm 0.5cm .45cm,clip=true]{images/numberjusticespro_coef_trend_linear.pdf} \\

 (e) Overruled Cases & (f) Difference in Years \\
\includegraphics[width = 0.475\textwidth, trim= 0.1cm 1cm 0.5cm .45cm,clip=true]{images/overruled_coef_trend_linear.pdf} & \includegraphics[width = 0.475\textwidth, trim= 0.1cm 1cm 0.5cm .45cm,clip=true]{images/yeardiff_coef_trend_linear.pdf} \\

   (g) Reciprocity & (h) Transitivity \\
\includegraphics[width = 0.475\textwidth, trim= 0.1cm 1cm 0.5cm .45cm,clip=true]{images/mutual_coef_trend_linear.pdf} & \includegraphics[width = 0.475\textwidth, trim= 0.1cm 1cm 0.5cm .45cm,clip=true]{images/triangle_coef_trend_linear.pdf} \\

    (i) Activity & (j) Popularity \\
\includegraphics[width = 0.475\textwidth, trim= 0.1cm 1cm 0.5cm .45cm,clip=true]{images/o2star_coef_trend_linear.pdf} & \includegraphics[width = 0.475\textwidth, trim= 0.1cm 1cm 0.5cm .45cm,clip=true]{images/i2star_coef_trend_linear.pdf} \\

@@

\begin{table}[H]
\centering
\begin{tabular}{rllll}
\hline \hline
 & mean & range & mean & range \\ 
  \hline
precision & 0.5872 & (0.5781, 0.5962) & 0.8622 & (0.8593, 0.8668) \\ 
  recall & 0.0565 & (0.0547, 0.0587) & 0.5839 & (0.5777, 0.592) \\ 
  F1 score & 0.103 & (0.1, 0.1069) & 0.6963 & (0.6915, 0.7027) \\ 
   \hline \hline
\end{tabular}
\caption{The predictive performance of the directed dyadic models with no trends, over ten 80/20 train/test splits.}
\label{tab:prediction_linear}
\begin{tabular}{rllll}
\hline \hline
 & mean & range & mean & range \\ 
  \hline
precision & 0.5589 & (0.5508, 0.5757) & 0.8677 & (0.865, 0.8718) \\ 
  recall & 0.098 & (0.0943, 0.103) & 0.5943 & (0.5887, 0.6032) \\ 
  F1 score & 0.1667 & (0.1618, 0.1748) & 0.7054 & (0.7013, 0.7119) \\ 
   \hline \hline
\end{tabular}
\caption{The predictive performance of the directed dyadic models with linear trends, over ten 80/20 train/test splits.}
\label{tab:prediction_linear}
\begin{tabular}{rllll}
\hline \hline
 & mean & range & mean & range \\ 
  \hline
precision & 0.6441 & (0.6302, 0.6536) & 0.8671 & (0.8626, 0.873) \\ 
  recall & 0.0852 & (0.0832, 0.0863) & 0.594 & (0.5874, 0.6012) \\ 
  F1 score & 0.1504 & (0.1473, 0.1525) & 0.705 & (0.7008, 0.712) \\ 
   \hline \hline
\end{tabular}
\caption{The predictive performance of the directed dyadic models with quadratic trends, over ten 80/20 train/test splits.}
\label{tab:prediction_quadratic}
\begin{tabular}{rllll}
\hline \hline
 & mean & range & mean & range \\ 
  \hline
precision & 0.642 & (0.6311, 0.6527) & 0.8664 & (0.8645, 0.8681) \\ 
  recall & 0.0866 & (0.0835, 0.0882) & 0.5947 & (0.591, 0.5978) \\ 
  F1 score & 0.1526 & (0.1475, 0.1552) & 0.7053 & (0.7026, 0.7079) \\ 
   \hline \hline
\end{tabular}
\caption{The predictive performance of the directed dyadic models with cubic trends, over ten 80/20 train/test splits.}
\label{tab:prediction_cubic}
\begin{tabular}{rllll}
\hline \hline
 & mean & range & mean & range \\ 
  \hline
precision & 0.645 & (0.635, 0.6668) & 0.8681 & (0.8639, 0.8712) \\ 
  recall & 0.0864 & (0.083, 0.0887) & 0.5955 & (0.5899, 0.6004) \\ 
  F1 score & 0.1524 & (0.1468, 0.1562) & 0.7064 & (0.7018, 0.7094) \\ 
   \hline \hline
\end{tabular}
\caption{The predictive performance of the directed dyadic models with quartic trends, over ten 80/20 train/test splits.}
\label{tab:prediction_quartic}
\end{table}
